


# Skin effect evaluation - report

***

&nbsp;

```{r, echo=FALSE,  warning = FALSE }

loc = (data_to_report()$well_location != "")
```


Evaluated on `r data_to_report()$time_project`.

Name of the well: `r data_to_report()$name`.

Location of the well: 


`r if(loc){ data_to_report()$well_location }`


&nbsp;
&nbsp;


The pumping test was evaluated to obtain the parameters of the aquifer and additional resistances. During the pumping test the pumped quantity was constant and the value was  **`r { data_to_report()$Q }` m3/s**. The well parameters are shown in Table 1 and aquifer parameters in Table 2.



&nbsp;
&nbsp;

```{r , echo=FALSE, comment = NA, warning = FALSE , fig.width = 11, fig.height = 4}

library(grid)
library(gridExtra)
library(gtable)
minus_res = 0
minus_res2 = 0
minus_res3 = 0



 value <- c( data_to_report()$R, data_to_report()$well_stor, data_to_report()$well_depth, data_to_report()$skin_faktor, data_to_report()$additional_resistance)
      units <- c("[m]",  "[-]", "[m]", "[-]", "[m]")
      names <- c( "Radius", "Storativity",  "Depth of well","SF", "S_skin" )
        
     
      table = data.frame(Value = value, Units = units)
      row.names(table) <- names
     
     value2 <- c(data_to_report()$Trans, data_to_report()$Stor, data_to_report()$hydraulic_cond, data_to_report()$cone_of_depr, data_to_report()$aqua_thick)
      units2 <- c("[m2/s]", "[m-1]", "[m/s]", "[m]", "[m]")
      names2 <- c("Transmissivity", "Storativity", "Hydraulic conductivity", "Cone of depression", "Aquifer thickness")
      
      na2 <- which(value2 > 0)
      value2 <- value2[na2]
      units2 <- units2[na2]
      names2 <- names2[na2]
      
      table2 = data.frame(Value = value2, Units = units2)
      row.names(table2) <- names2

title <- textGrob("Table 1. well parameters",gp=gpar(fontsize=15))
title2 <- textGrob("Table 2. aquifer parameters",gp=gpar(fontsize=15))

tt3 <- ttheme_minimal(base_size = 12.5,
  core=list(bg_params = list(fill = blues9[2:5], col=NA)))

t1 <- tableGrob(table, rows = names, theme =  tt3)
t2 <- tableGrob(table2, rows = names2, theme = tt3)

padding <- unit(2,"mm")

table <- gtable_add_rows(
     t1, 
     heights = grobHeight(title) + padding,
     pos = 0)

table2 <- gtable_add_rows(
     t2, 
     heights = grobHeight(title2) + padding,
     pos = 0)

table <- gtable_add_grob(
    table, 
    title, 
    1, 1, 1, ncol(table))

table2 <- gtable_add_grob(
    table2, 
    title2, 
    1, 1, 1, ncol(table2))


# grid.arrange(
 # table,
 # table2,
 # respect=TRUE,
 # nrow = 1)

grid.arrange(
 table,
 table2,
 respect = TRUE,
 layout_matrix = matrix(c(1, 2), byrow = TRUE, nrow = 1),
widths = c(7,7), heights = c(3,3)
 )

```




```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
raw = sum(data_to_report()$report_contain == "Graph - input data") == 1
```


```{r, eval = raw, echo=FALSE,  warning = FALSE, fig.align ='center'}
asis_output("###  Graph - input data" )
```
&nbsp;

```{r , eval = raw, collapse=TRUE, echo=FALSE,comment = NA, out.width = '585px', out.height = '585px', fig.align ='left', warning = FALSE }

  dat_slope(first_straight_section(data_ok(), section_first()))
         
     plot_data =   (ggplot(data = data_ok()[1:end_t(),], aes(x = time,
                                                     y = drawdown)) +
              geom_point() + scale_x_log10() +
              labs(x = "Time", y = "Drawdown") +
              geom_abline(
                aes(
                  slope = as.numeric(dat_slope()$coefficients[2]),
                  intercept = as.numeric(dat_slope()$coefficients[1]),
                  color = "slope"
                )
              ) +
              labs(color = "")
                  +
              
              theme(legend.position = "bottom")
            
          
     +
              theme(plot.title = element_text(size = 18)) +
              theme(text = element_text(size = 16))
      +
             theme(
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               panel.background = element_blank(),
               axis.line = element_line(colour = "black")
             ) 
     )
          

plot_grid(plot_data,  ncol = 1, scale = 1)

```

&nbsp;

```{r, collapse=TRUE, echo=FALSE, comment=NA, tidy=FALSE}
data_fit = sum(data_to_report()$report_contain == "Graph - data used - Cd") == 1
```


```{r, eval = data_fit, echo=FALSE,  warning = FALSE, fig.align ='center'}
asis_output("###  Graph - data used for well storativity evaluation" )
```


&nbsp;


```{r , eval = data_fit, collapse=TRUE, echo=FALSE,comment = NA, out.width = '585px', out.height = '585px', fig.align ='left', warning = FALSE }

used_max = data_to_report()$max_data_used
max_y = data_ok()[40,2]
         max_x = data_ok()[40,1]

plot.data_used <-  (ggplot(data = data_ok()[1:40,], aes(x = time,
                                                     y = drawdown)) +
              geom_point() +
              
              scale_y_log10() +
              scale_x_log10()+
              
              labs(color = "") +
              
              geom_point(
                data = data_ok()[slider_well_storativity_val()[1]:slider_well_storativity_val()[2], ],
                aes(x = time,
                    y = drawdown,
                    color = "Selected - well storativity"
                    )
              )            +
                
              scale_color_manual(values = "red")
            
            +
              
              theme(legend.position = "bottom")
            
                        + 
            
              labs(x = "Time", y = "Drawdown") 
            +
              
              theme(plot.title = element_text(size = 18)) +
              theme(text = element_text(size = 16)) 
        
      
           +
             theme(
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               panel.background = element_blank(),
               axis.line = element_line(colour = "black")
             )
            
            
          )
plot_grid(plot.data_used,  ncol = 1, scale = 1)

```

